A thesis draft

### 2018-10-10 draft.tex
Add content about MANO and VNFs

\begin{itemize}
 \item Network Function Virtualization Infrastructure (NFVI): it's the heart of 
the whole computation component, and here three sub-domains can be identified:
\todo{Expand this section}
\begin{itemize} 
 \item \textbf{Hypervisor domain} that is composed of the Virtual Compute, the 
Virtual Storage, and the Virtualization Layer. These components are used to 
virtualize the computational and storage resources, providing a layer for 
accessing it.
 \item \textbf{Compute domain} composed by the Physical Compute and the 
Physical Storage. These are the real resources which are virtualized via 
software.
 \item \textbf{Infrastructure domain} which has the Physical Network, and its 
virtualized counterpart as made available by the Virtualization Layer.
\end{itemize}

@@

\item VNFs this are the core components that perform packets manipulation 
\todo{Expand}

\item NFV Management and Orchestration (MANO) \todo{Expand this part}

>>>>

\begin{itemize}
 \item \textbf{Network Function Virtualization Infrastructure (NFVI)}: it's the
   heart of the whole computation component, and here three sub-domains can be
   identified: \todo{Expand this section}
\begin{itemize} 
 \item \textbf{Hypervisor domain} that is composed of the Virtual Compute, the
   Virtual Storage, and the Virtualization Layer. These components are used to
   virtualize the computational and storage resources, providing a layer for
   accessing it.
 \item \textbf{Compute domain} composed by the Physical Compute and the 
Physical Storage. These are the real resources which are virtualized via 
software.
 \item \textbf{Infrastructure domain} which has the Physical Network, and its 
virtualized counterpart as made available by the Virtualization Layer.
\end{itemize}

@@

\item \textbf{VNFs} this are the core components that perform packets
  manipulation. This components are design to be lightweight services able to
  elaborate a great amount of packets per seconds. Manupulation can be of two
  typologies: stateful or stateless. In the first case, a state is maintained,
  and the VNF can perform heuristics about data coming through it (especially
  useful to detect patterns in the data flow, e.g. DDos attacks). In the second
  case, no state is maintained, and every packet is treated without any
  particular assumption. \todo{Add ref to chap about SFC?}

\item \textbf{NFV Management and Orchestration (MANO)} also known as NFV
  Orchestrator (NFVO) is responsible for the end-to-end management and
  orchestration of network services (NS), also called SFC. The MANO has
  different responsabilities, such as managing the
  istantiation/destruction/modification of the SFCs, that achieves interacting
  with the VIM. \todo{Expand this part}
